Twists of supersymmetric gauge theories

### 2019-11-11 paper.tex
4d 6d

The generalized $\beta\gamma$ system is a special case of generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.

\brian{Should we say something about how the holomorphic theories couple here?}

@@

@@

\begin{thm}
The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
\end{align*}
satisfies the classical master equation
\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
\label{thm:vectormultipletSUSY}
\end{thm}

@@

A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
Let $S_-^{6d}$ be the negative $\so(6)$ irreducible spin representation and suppose $R$ is a (complex) symplectic $\fg$-representation, with symplectic pairing labeled by $\<-,-\>_R$. 
The BRST fields of the $(1,0)$ hypermultiplet consist of a $W \otimes R$-valued scalar
\[
\phi \in \Omega^0(\RR^6) \otimes W \otimes R
\]
and an $R$ valued negative Weyl spinor
\[
\psi_- \in \Omega^0(\RR^6) \otimes S_-^{6d} \otimes R .
\]
Denote the induced symplectic pairing on $W \otimes R$ by $\<-,-\>_{W \otimes R}$. 
The action of the free hypermultiplet is given by
\[
S_{\rm matter} (\phi, \psi_-) = \frac{1}{2} \int_{\RR^6} \d^6 x \; \<\partial_{x_i} \phi , \partial_{x_i} \phi\>_{W \otimes R} + \frac{1}{2} \int_{\RR^6} \d^6 x \;\<\psi_-, \sd \dd \psi_-\>_R .
\]

The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q) & = \int \<\phi^*, (Q, \psi_-)\>_{W \otimes R} + \int \<\psi^*_-, \rho(\d \phi) Q\>_R \\
I^{(2)} (Q_1 \otimes Q_2) & = \int \<\psi^*_- , \rho(\Gamma(Q_1, Q_2)) \psi_-\>_R 
\end{align*}
where we recall that the pairing is of the form $\Gamma : \Sigma^{\otimes 2} = (S_+ \otimes W)^{\otimes 2} \to V$. \brian{I'm also using $(S_+)^* = S_-$.}
These functionals provide an off-shell action of $\cN = (1,0)$ supersymmetry on the free hypermultiplet, as the following proposition shows.
Below, $\fL_{\rm matter}$ is the abelian local Lie algebra describing the free hypermultiplet, and $\mf A$ is the $(0,1)$ supertranslation algebra.  
As always, $I_{\rm Poin}$ is the action functional encoding ordinary Poincar\'{e} invariance.

\begin{prop}[\cite{SWchar}]
The functional
\[
\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm matter}) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS_{\rm matter} + \frac{1}{2} \{\fS_{\rm matter}, \fS_{\rm matter}\} \right) = 0 .
\]
\end{prop}
\begin{proof}
\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
\end{proof}

Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
\[
\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
\]
where $W$ is a (complex) $2$-dimensional symplectic vector space. 
The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
\end{align*}
These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, which we proved above in Theorem \label{SUSY_YM_theorem}, and state below as a proposition. 
Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.

 implies the following proposition for $6d$
\begin{prop}[special case of Theorem \ref{SUSY_YM_theorem}]
The functional
\[
\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
\]
\end{prop}

@@

\subsubsection{$\cN=1$ SYM with matter}

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
The field content for the BRST fields in the gauge sector is:
\[
(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
\]

For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
\[
(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
\]

Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.

The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
\end{align*}
\brian{add terms involving antifields}
\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter. My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
}

The action
\[
S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) 
\]
is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
\end{align*}
where $Q_\pm \in S_{\pm}$. 
As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
\[
I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
\]

The action of supersymmetry on the gauge sector is encoded by the functionals:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
\end{align*}
\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
Such terms would turn this acyclic.
Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
}

These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.

%The result appears in \cite{SWchar}, and we do not repeat the proof here.

\begin{prop}[\cite{SWchar}]
Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
Then, the functional
\[
\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
\]
\end{prop}

Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.

\begin{proof}
Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.

First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
\[
\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
\]
So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.

The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
\end{align*}
The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
\begin{align*}
\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+)) 
\end{align*}
\brian{Get the signs right and these terms should cancel.}

The computation of the remaining terms in the matter sector are summarized in the following lemma. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
\]
\end{lem}
\brian{extra terms in $I^{(2)}$?}
\begin{proof}

First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
\[
\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
\]
We first focus on terms involving variations of $\phi, \Bar{\phi}$:
\begin{align*} 
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
\end{align*}
In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.

Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
Thus, this calculation implies
\[
\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
\]
for all $Q_\pm, Q_\pm'$.

Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$. 
We must show
\[
\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
\]
for all $Q_\pm, Q_\pm'$.

We start by computing the variation of $\psi_+ + \psi_-$:
\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}

>>>>

\begin{rmk}
This is a special case of generalized BF theory:
the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
\end{rmk}

@@

\subsubsection{The free scalar and free fermion}

\brian{does this warrant it's own definition?}

@@

\begin{thm}
The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
\brian{Where is the Poincare part?}
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
\end{align*}
satisfies the classical master equation
\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
\label{thm:vectormultipletSUSY}
\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
\end{thm}

@@

@@
